%-*- coding:UTF-8 -*-
% dna-align.tex
\documentclass[hyperref,UTF8]{ctexart}
\usepackage{geometry}
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{amsthm}
\usepackage{listings} %插入代码
\usepackage{xcolor} %代码高亮
\usepackage{blkarray}
\usepackage{diagbox}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage{color}
\usepackage{multirow}
\usepackage[all,pdf]{xy}
\usepackage{verbatim}   %comment
\usepackage{cases}
\usepackage{clrscode3e}	% need clrscode3e package which is not included in CTex.
\usepackage{hyperref}

\geometry{screen}
\hypersetup{
    colorlinks=true,
    bookmarks=true,
    bookmarksopen=false,
    pdfpagemode=FullScreen,
    pdfstartview=fit,
    pdftitle={DNA-Align},
    pdfauthor={Trasier}
}

% THEOREM Environments --------------------------------------------------------
\newtheorem{thm}{Theorem}[subsection]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{prob}[thm]{Problem}
\newtheorem{mthm}[thm]{Main Theorem}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\theoremstyle{remark}
\newtheorem{rem}[thm]{Remark}
\numberwithin{equation}{subsection}
% MATH ------------------------------------------------------------------------
\DeclareMathOperator{\RE}{Re}
\DeclareMathOperator{\IM}{Im}
\DeclareMathOperator{\ess}{ess}
\newcommand{\eps}{\varepsilon}
%\newcommand{\To}{\longrightarrow}  conflict with \package{clrscode3e}p
\newcommand{\h}{\mathcal{H}}
\newcommand{\s}{\mathcal{S}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\W}{\mathcal{W}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\BOP}{\mathbf{B}}
\newcommand{\BH}{\mathbf{B}(\mathcal{H})}
\newcommand{\KH}{\mathcal{K}(\mathcal{H})}
\newcommand{\Real}{\mathbb{R}}
\newcommand{\Complex}{\mathbb{C}}
\newcommand{\Field}{\mathbb{F}}
\newcommand{\RPlus}{\Real^{+}}
\newcommand{\Polar}{\mathcal{P}_{\s}}
\newcommand{\Poly}{\mathcal{P}(E)}
\newcommand{\EssD}{\mathcal{D}}
\newcommand{\Lom}{\mathcal{L}}
\newcommand{\States}{\mathcal{T}}
\newcommand{\abs}[1]{\left\vert#1\right\vert}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\left<#1\right>}
\newcommand{\norm}[1]{\left\Vert#1\right\Vert}
\newcommand{\essnorm}[1]{\norm{#1}_{\ess}}


% Some setup
\pagestyle{plain}
\geometry{a4paper, top=2cm, bottom=2cm, left=2cm, right=2cm}
\CTEXsetup[format={\raggedright\bfseries\Large}]{section}
\lstset{numbers=left, %设置行号位置
        numberstyle=\small, %设置行号大小
        keywordstyle=\color{blue}, %设置关键字颜色
        commentstyle=\color{purple}, %设置注释颜色
        %frame=single, %设置边框格式
        escapeinside=``, %逃逸字符(1左面的键)，用于显示中文
        breaklines, %自动折行
        extendedchars=false, %解决代码跨页时，章节标题，页眉等汉字不显示的问题
        %xleftmargin=2em,xrightmargin=2em, aboveskip=1em, %设置边距
        tabsize=4, %设置tab空格数
        showspaces=false %不显示空格
       }

% About math
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Emph}{\textbf}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcommand{\resetcounter}{\setcounter{equation}{0}}
\newcommand{\equsuf}[1][x]{\equiv_{\textit{Suff(#1)}}}	
\newcommand{\Suff}{\textit{Suff}}
\newcommand{\len}[1][x]{\textit{length}_{#1}}

% section deeep to 3 1.1.1
\setcounter{secnumdepth}{3}

\begin{document}

\title{\Huge DNA-Align}
\vspace{2cm}
\author{\Large Trasier}
\date{\today}
\maketitle

\section{Problem Statement}
\label{sec:problem_statement}
	
	There are two major challenges within the alignment problem that we hope you will address in this competition:
	\begin{enumerate}
	
		\item \Emph{A Read May Not Perfectly Match the Reference.}
		A fraction of the reads will have no exact substring match in the reference due to genetic
		variation and sequencing errors.
		Although it is possible to obtain the exact alignment of two strings via the
        \href{https://en.wikipedia.org/wiki/Smith-Waterman_algorithm}{Smith-Waterman} or
        \href{https://en.wikipedia.org/wiki/Needleman-Wunsch_algorithm}{Needleman-Wunsch}
		algorithms, this procedure runs in time proportional to the product of the strings' lengths;
		In theory, this could be done for every read, but would be computationally infeasible.
		
		\Emph{There is no known efficient solution to inexact substring matching.}
		
		\item \Emph{Matching May be Ambiguous.}
		Portitions of the genome are highly-repretitive.
		In extreme cases, thousands of characters may be repeated thousands of times.
		It is impossible for 150 character reads to unambiguously map to these regions,
		but is is very important to know that the reported match may not be accurate.
		
		\Emph{The aligned must accurately measure the ambiguity of each mapping and report via a mapping confidence score.}
		
	\end{enumerate}

	
\section{Data Description}
	
	For the competition, submissions will be provided with same reference genome and new set of simulated reads.
	Each submission will undergo up to threee competition tests with increasing difficulty,
	with access to more difficult tests contingent on adequate performance on easier tests.
	The tests differ in complexity by the number of reads to be aligned and
	the number of chromatids the reads are to be aligned to.
	
	\begin{enumerate}
	
		\item \Emph{Small test}
		
		Chromosome 20($6.4\times10^7$ characters), up to $10^4$ read pairs
		
		\item \Emph{Medium test}
		
		Chromosomes $1, 11, 20$($4.5\times10^8$), up to $10^6$ read pairs.
		
		\item \Emph{Large test}
		
		Chromosomes $1, 2, \cdots, 24$($3.2\times10^9$), up to $10^7$ read pairs.
		
	\end{enumerate}
	
\section{Functions}
	
	The example and provisional test case will contain two tests with different difficuly(small, medium)
	while the system test case will contain three tests(small, medium large).
	The DNASequencing class won't be reinstantiated between the small and medium tests.
	For the large system test, solutions will be run stand-alone outside of the normal submission
	system on VMs with similar characteristics to the test processors.
	
	This set of functions will be called at most 2 times from smaller test to bigger ones.
	For large system tests, it will only be called once.
	Functions call order for a test within a testcase as follows:
	\begin{enumerate}
	
		\item --- Preprocessing time limit starts counting here
		
		\item int \proc{initTest}(int testDifficulty)
		
		testDifficulty can be 0: small, 1: medium, 2: large. Return can be any valid integer.
		
		\item int \proc{passReferenceGenome}(int chromatidSequenceId, string[] chromatidSequence)
		
		will be called 1, 3 or 24 times according to the test difficuly. Return can be any valid integer.
		
		\item int \proc{preProcessing}()
		
		Return can be any valid integer.
		
		\item --- Preprocessing time limit ends here
			  --- Time Cutoff starts counting here (the time used for scoring)
			
		\item string[] \proc{getAlignment}(int N, double normA, double normS, string[] readName, string[] readSequence)
		
		will be called once per test case.
		
		N is the number of reads in the test.
		Both array will contain exactly N elements as well as the retrun array.
		Elements at (2*i) and (2*i+1) are representing a read pair.
		
		Format of the return string:
		
		ReadName,\ ChromatidSequenceId,\ Start position(1-based),\ End position(1-based), strand(reference [+] or reverse complement [-]), mapping confidence score	\\
		"sim1/1,1,10000,10149,+,0.89"
		
		\item --- Time Cutoff ends here
			
	\end{enumerate}

\section{Notes}	
\label{sec:notes}

	\begin{itemize}
	
		\item Memory limit is 16GB
		
		\item Test processors are AWS m3.2xlarge instances
		
		\item There is no explicit code size limit. The implicit source code size limit is around 1MB
		(it is not advisable to submit codes of size close to that or large). The compilation time limit is 60 seconds.
		
		\item You will be allowed to make example submissions each \Emph{30 minutes} and provisional submissions \Emph{each 3 hours}.
		
	\end{itemize}
	
	
\section{Observation}
\label{sec:observation}
	
	\begin{enumerate}
		
		\item \Emph{Ground truth}中的read对是否一个为[+],另一个为[-]
		
		结果是成对出现的

		\item \Emph{Ground truth}中的$end\_position - start\_position$的长度是否一定为150
		
		不一定，结果在$[110, 348]$之间

		\item \Emph{Ground truth}中的read对的间距情况
		
		结果在$[171, 542]$之间
	
		\item $[-]$是否表示原串的$\Emph{Reverse Complement}$
		
		确实是
				
		\item 染色体的中间是否含有未定义字符
		
		\Emph{smallCase}不含有

		\item \Emph{Ground truth}中read的得分是多少，是否可以找到阈值
		
		显然存在\kw{insert}和\kw{delete}，导致计分有问题
		
		\item 统计子串频度
		
		暂时没统计
	
	\end{enumerate}
	
\section{Thought}
\label{sec:thought}
	
	初始算法
	\begin{enumerate}
	
		\item 如何表示染色体
		
		\begin{enumerate}[(1)]
		
			\item 完整的字符串
			
			\item 使用子串重排序列

			\item 切片策略
			
			即将染色体每隔若干长度切片，然后存入trie树中，显然所有的字串应该等长，若长度不够则加入$U$填充。
			trie可以将染色体压缩，同时根据$AGCT$的分布信息可以一定程度上减枝。
			
		\end{enumerate}

		\item 如何剪枝
		
		\begin{enumerate}[(1)]
		
			\item 根据染色体的$AGCT$数量与当前基因片的$AGCT$数量的\Emph{余弦相似度}
			
			\item 根据子序列的$AGCT$数量与当前基因片的$AGCT$数量的\Emph{欧式距离}
			
			\item 根据子串的分布于当前基因片的子串的分布
		
		\end{enumerate}
		
		\item 如何计算\Emph{Confidence}

		每个染色体的命中概率，训练数据可得。
		横跨两个slice的概率，测试可得。
		
		\item 如何利用$|truth_st-st| \ge 300$
		
		\item 如何降低时间复杂度

		改进needlman的算法，因为Insert和Delete至多为2，因此原来的$O(n^2)$的算法可以改进为$O(5n)$的算法，实测性能很好。
		非常适合处理多chromat的情况。

		\item 适合降低空间复杂度

		尽可能将原染色体切片，每个slice长度至少为read长度，即150。那么显然有一定的概率最佳匹配横跨两个切片，并且至多横跨两个。
		这显然是一个概率问题，可以根据此推断\Emph{Confidence}。同时，考虑增加一倍的偏置，可以提高准确率，但是并不增加时间复杂度。
		trie的叶子结点存储acgt的数量，显然可以根据\Emph{余弦相似度}或者\Emph{欧式距离}做初步剪枝。
		当然同一个切片可能属于不同染色体不同位置，这显然也是个概率问题，所幸染色体并不多。这个还是可以做做的。
		$3.2 \times 10^10 = 32G$可以大幅度压缩，并且$320M \times |node|$的结点信息存储应该还是可行的。
		余下的问题，就是使用核心算法对当前路径进行匹配，记分。

		\item 如何处理\Emph{Reverse Complement}
		
		将read串反转测试。
	
	\end{enumerate}
	
	算法v1.0的核心问题是无论怎么样都太慢了，有几个主要因素导致速度上不去
	\begin{enumerate}
	
		\item 仅考虑频度剪枝的力度太小了
		
		通过查看染色体的频率可以知道24个染色体的ACGT的分布相对平均，
		这说明ACGT的分布是平均的。那么，仅考虑ACGT的数量作为剪枝几乎没有什么效果。
		同时，考虑read的数量起始并不小。
		通过将needlman的算法修改为$O(n)$，显然一遍read检测的时间为$O(n) \times 10^4 = 3\times10^6$，
		这意味着我们剪枝的力度决定了算法的时间效率。
		个人感觉，平均200-300次检测就要超时了。
		
		\item 空间压缩显然不够
		
		原因就是trie大稀疏了，显然越靠近根结点压缩效率越高。
		但是越远离根结点，它越稀疏，再考虑到结点的大小，\Emph{MD}，还不如直接留在内存里。\\
		\Emph{Mother Fucker}。\\
		其实可以用trie的森林解决这个问题，
		但是还是怀疑能不能降低空间复杂度
		
	\end{enumerate}
	
	新的想法
	\begin{enumerate}

        \item 如何切片

    	统计长度为$10-30$的高频的串的长度，显然这个可以利用trie预处理。
    	同时，我们将read按照这个长度分片。我们的思路是什么？
    	显然，将其对应的基因都进行切片后，切片的得分加成近似于这个read的加成。
    	因为高频的串可以事先计算相似值。所以，这个统计和计算应该更快点儿。


	\end{enumerate}
	
	困扰我的问题
	\begin{enumerate}
	
		\item 如何快速地确定染色体
		
		不能快速定位染色体是一件非常恶心的事儿，因为，这样就意味着至少$O(24)$
		这样级数的遍历，然而，代码质量不高的话。很有可能这就是个$O(10^2)$的级数。
		
		\item 如何快速地定位基本位置
		
		最短的染色体是21号染色体，长度为$46,709,983 = 4 \times 10^7$这个量级的级数。
		如何能快速地定位到某个区间是关键。如果把每对read看成一个整体，
		这意味着我需要把长度为300的字符串定位到$[4\times10^7, 2\times10^8]$
		这样量级的染色体上，显然差了两个量级。
		不能快速地定位，往往意味着需要额外开销暴力的定位到某个区间。
		
		\item 如何压缩存储
		
		所有的问题都归结为内存放不下$32G$的东西，如何把这样一个字符串进行
		压缩绝对是关键。
		
	\end{enumerate}
	
	拟定的解决策略
	\begin{enumerate}
		
		\item 根据切片分类
		
		分类这个东西绝逼是个不靠谱的，但是没办法。
		得赶紧弄个solution。
		基本思路，字符串太长的好处是，很短的串的权重非常小，出现的频度非常高。
		那么，我们假设长度为10的子串刚刚好。
		以10为单位长度将原染色体拆分，构建trie。
		这个trie树是一定不超过内存的，而且占用预处理时间，所以可以尽量长。
		那么如何表示原串呢？
		原串变成了一堆指针序列。
		
		\item 快速定位
		原串是一个指针序列，表示的全部是叶子。各个nxt数组存的全部是当前路径的
		acgt总量。这显然构成了一个滑动窗口。
		我整体的read长度约为600，即2倍自身长，匹配染色体的一部分。
		每边的acgt距离差保证在3以内。
		
		若暴力枚举的复杂度为$6e^6 \times 10^4 = 6e^{10}$。
		这还是太慢了，如果可以降低为$6e^9 \~ 6e^8$就是个很好的时间复杂度了。
		
		\item 
		
	\end{enumerate}
	
	
\end{document}

